\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning the paper adding some extra info

This The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media

The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain. The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern. Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.

\medskip
Fluid $1$ is introduced from the left hand side of the formation. Later, different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied. Boundary conditions will include a no-slip condition for the upper and lower boundary inlet is place at the left hand side while outlet on the right hand side of the domain. Initial conditions include initial values of velocity and pressure in the left and right hand side of the domain respectively. Also for different cases we have different geometrical domain aspect ratios, number of elements and types of grid (fixed and usntructured or adaptive and unstructured mesh will be used). 
%\noindent One more case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}.
A domain consisting of $4$ square regions in which each quarter is represented by a permeability value (Fig.\ref{fig:square}a) and $1$ value of different permeabilities (K is represented by the blue and red shaded square areas) as well as it is fully saturated with fluid $2$. At the upper and lower sides of the domain no-slip boundary condition is applied. The left hand side of the domain is defined as the inlet for fluid $1$ which is introduced along this side with a velocity of $u=1$. The right hand side is the outlet and pressure is set to $0$. Fluid $1$ across the left hand side of the domain is trying to displace the existing fluid $2$. What can been seen here is a cross flow case as the flow passes through different regions and evolves. The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$ (Fig.\ref{fig:square}b).

@@

\medskip
A slightly modified test-case (see fig.\ref{fem_cv_represent_a}) 
with similar initial and boundary conditions, but in this set of simulations the geometrical aspect ration is $2$ is following. The model was also qualitatively validated against laboratory experiments conducted by \citet{evans_1994}. The last set of simulations as this is described in Fig.\ref{fig:1testcase} is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.

@@

\medskip
As can been seen from the Fig.\ref{fig:1a_homoheleshaw_3},\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3} there is a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$ under the same number of elements. Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3}, \ref{fig:1c_homoheleshaw_3} give a description of the Hele-Shaw cell simulation when $MR=10$ followed by the same initial and boundary conditions set-up, but now for the Hele-Shaw case of a heterogeneous formation as this is described in Figures \ref{fig:3a_heteheleshaw_10},\ref{fig:3b_heteheleshaw_10},\ref{fig:3c_heteheleshaw_10}. Fingers will be more profound and will start develop faster when the $MR=10$ compared to the uniform front that is developing when the $MR=3$ for the same time steps. In addition the flow patter of the fingers will be sharper and more intense when different regions with different permeabilities are introduced in the formation. The importance of this set-up is to understand how the simulation works and if the result that will produced reagarding the development and pattern of the fingers, actually follow the experimental results  and how this is developed under different permeability schemes as these has already been experimentaly tested.

@@

\medskip
Having already verified that model is working for the hele-shaw experimental test-cases, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities. Initial and boundary conditions are described in Fig. \ref{fig:testcase_heter_domain}, while inlet velocity is $u=1$ on the left hand side and the pressure set to $0$ on the outlet. A quick reminder at this point is that the simulator we are testing has also options to introduce gravity and/or corriolis, but for this current set of simulations these are neglected. What is expected is a significant growth of fingers when comparing mobility ratios that differ an order of magnitude (Fig.\ref{fig:1testcase}). The next step is a comparison under the same mobility ratio of $10$, using the fixed and the adaptive mesh. For the fixed mesh we have $4600$ elements, but for the adaptive mesh we start with $400$ up to $600$, depends how fine we would like the mesh to be, and we reach up to $24000$. %Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used. 
Figures \ref{fig:2testcase_a}, \ref{fig:2testcase_b}, \ref{fig:2testcase_c} and \ref{fig:2testcase_d} will give a description of the simulation for different time-steps as these are described. In this set the interfacial instability is becoming more profound as the flow develops. Based on these two cases so far, an initial relation between the quantitative and qualitative outcome of our simulations can be derived. Fingers will develop faster in areas where permeabilities are higher. This can be seen from the overall sharp increase of velocity magnitude during the injection of the fluid $1$.

>>>>

\medskip
The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media.The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain. The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern. Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.

\medskip
Fluid $1$ is introduced from the left hand side of the formation. Later, different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied. Boundary conditions will include a no-slip condition for the upper and lower boundary inlet is place at the left hand side while outlet on the right hand side of the domain. Initial conditions include initial values of velocity and pressure in the left and right hand side of the domain respectively. Also for different cases we have different geometrical domain aspect ratios, number of elements and types of grid (fixed and usntructured or adaptive and unstructured mesh will be used). 
%\noindent One more case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}.
A domain consisting of $4$ square regions in which each quarter is represented by a permeability value (Fig.\ref{fig:square}a) and $1$ value of different permeabilities (K is represented by the blue and red shaded square areas) as well as it is fully saturated with fluid $2$. At the upper and lower sides of the domain no-slip boundary condition is applied. The left hand side of the domain is defined as the inlet for fluid $1$ which is introduced along this side with a velocity of $u=1$. The right hand side is the outlet and pressure is set to $0$. Fluid $1$ across the left hand side of the domain is trying to displace the existing fluid $2$. What can been seen here is a cross flow case as the flow passes through different regions and evolves. The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$. %\ref{fig:square}b).

@@

\medskip
A slightly modified test-case (see fig.\ref{fem_cv_represent_a}) with similar initial and boundary conditions, but in this set of simulations the geometrical aspect ration is $2$ is following. The model was also qualitatively validated against laboratory experiments conducted by \citet{evans_1994}. The last set of simulations as this is described in fig.\ref{fem_cv_represent_a}c is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.

@@

\medskip
As can been seen from the fig.\ref{fig:1a_homoheleshaw_3}-\ref{fig:1c_homoheleshaw_3} there is a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$ under the same number of elements. %Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3}, \ref{fig:1c_homoheleshaw_3} 
They also provide the reader with a description of the Hele-Shaw cell simulation when $MR=10$ followed by the same initial and boundary conditions set-up, but now for the Hele-Shaw case of a heterogeneous formation as this is described in figures \ref{fig:3a_heteheleshaw_10} %\ref{fig:3b_heteheleshaw_10}
-\ref{fig:3c_heteheleshaw_10}. Fingers will be more profound and will start develop faster when the $MR=10$ compared to the uniform front that is developing when the $MR=3$ for the same time steps. In addition the flow patter of the fingers will be sharper and more intense when different regions with different permeabilities are introduced in the formation. The importance of this set-up is to understand how the simulation works and if the result that will produced reagarding the development and pattern of the fingers, actually follow the experimental results  and how this is developed under different permeability schemes as these has already been experimentaly tested.

@@

\medskip
Having already verified that model is working for the hele-shaw experimental test-cases, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities. Initial and boundary conditions are described in fig.\ref{fig:testcase_heter_domain}, while inlet velocity is $u=1$ on the left hand side and the pressure set to $0$ on the outlet. A quick reminder at this point is that the simulator we are testing has also options to introduce gravity and/or corriolis, but for this current set of simulations these are neglected. What is expected is a significant growth of fingers when comparing mobility ratios that differ an order of magnitude (Fig.\ref{fig:1testcase}). The next step is a comparison under the same mobility ratio of $10$, using the fixed and the adaptive mesh. For the fixed mesh we have $4600$ elements, but for the adaptive mesh we start with $400$ up to $600$, depends how fine we would like the mesh to be, and we reach up to $24000$. %Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used. 
Figures \ref{fig:2testcase_a}, \ref{fig:2testcase_b}, \ref{fig:2testcase_c} and \ref{fig:2testcase_d} will give a description of the simulation for different time-steps as these are described. In this set the interfacial instability is becoming more profound as the flow develops. Based on these two cases so far, an initial relation between the quantitative and qualitative outcome of our simulations can be derived. Fingers will develop faster in areas where permeabilities are higher. This can be seen from the overall sharp increase of velocity magnitude during the injection of the fluid $1$.
